### 2017-08-30 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

\textbf{Solution:} 
\begin{proof}
\textbf{Uniqueness:} \\
Assume there exists two field isomorphisms $f_1, f_2$ from $\mathcal{F}_1$ onto $\mathcal{F}_2$. Let $E$ is an upper bounded set in $\mathcal{F}_1$, and according to the Completeness Axiom, it's supremum is $e$. Denote $E_1 = f_1(E)\in \mathcal{F}_2, E_2 = f_2(E)\in\mathcal{F}_2$. Then according to properties of isomorphism, $E_1, E_2$ are both upper bounded sets, so they both have supremums, denoted by $e_1, e_2$. Then since the isomorphism preserves the order, we have $f_1(e) = f_2(e) = e_1 = e_2$. Since for each $x\in \mathcal{F}_1$, we can construct a set with $x$ being it's supremum (for example, a sequence converge to $x$), we have $f_1(x) = f_2(x)$. Thus $f_1 = f_2$. \\[5pt]
\textbf{Existence:} \\

>>>>

\textbf{Solution:} 
\begin{proof}
\textbf{Uniqueness:} \\
Assume there exists two field isomorphisms $f_1, f_2$ from $\mathcal{F}_1$ onto $\mathcal{F}_2$. Let $E$ is an upper bounded set in $\mathcal{F}_1$, and according to the Completeness Axiom, it's supremum is $e$. Denote $E_1 = f_1(E)\in \mathcal{F}_2, E_2 = f_2(E)\in\mathcal{F}_2$. Then according to properties of isomorphism, $E_1, E_2$ are both upper bounded sets, so they both have supremums, denoted by $e_1, e_2$. Then since the isomorphism preserves the order, we have $f_1(e) = f_2(e) = e_1 = e_2$. Since for each $x\in \mathcal{F}_1$, we can construct a set with $x$ being it's supremum (for example, a sequence converge to $x$), we have $f_1(x) = f_2(x)$. Thus $f_1 = f_2$. \\[5pt]
\textbf{Existence:} \\
Since $\mathcal{F}_1, \mathcal{F}_2$ are fields, they close to multiplications. Let $I_1$ be the identity of $\mathcal{F}_1$, and $I_2$ be the identity of $\mathcal{F}_2$. Then since each non-zero element have an inverse, we can define rational numbers in $F_i$:
$$
q = (c_1I_i)\times (c_2I_i)^{-1},
$$
where $x^{-1}$ means the inverse in it's field. \\
Now we construct the map like this: \\
$$
\begin{aligned}
f: ~\mathcal{F}_1&\to\mathcal{F}_2 \\
(c_1I_1)\times(c_2I_1)^{-1} &\mapsto (c_1I_2)\times(c_2I_2)^{-1}.
\end{aligned}
$$
For $x \in \mathcal{F}_1$, if $x$ is not a rational number, we call it an irrational number. If $x$ is an irrational number, if we can construct two monotone sequences of rational numbers ${a_i}, {b_i}$, s.t. $a_{i+1}>a{i}$, $b{i+1} < b{i}$, and ${a_i}, {b_i} \to x$, then since the map preserves the order for rational numbers, we can define 
$$
f(x) = \lim_{i\to\infty}f(a_i) = \lim_{i\to\infty}f(b_i).
$$
for irrational numbers. Then using the linear property of limit, it is trivial to prove that this function is a field isomorphism.

First we prove that $\mathcal{F}$ has the Archimedean property. If not, suppose for $a, b\in \mathcal{F}$, there do not exist a natural number n, $n\cdot a > b$. Suppose $E$ is a bounded set, and $b \in E$, while $a \notin E$. According to the Completeness Axiom, $E$ has a supremum, denoted by $x_0$.

suppose $E$ is a bounded set in $\mathcal{F}$, and with the completeness property, $E$ has a supremum, denoted by $x_0$. 
According to properties of ordered field, there exists $a_0$,
